---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# convexity

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/92amartins/convexity/branch/master/graph/badge.svg)](https://codecov.io/gh/92amartins/convexity?branch=master)
<!-- badges: end -->

The goal of convexity is to provide hints for stock market investments.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("92amartins/convexity")
```

## Examples

Here are some use cases supported by the package.

Using the `stock()` function, you get back a `data.frame` suitable for any financial analysis.

```{r stock, warning=FALSE}
library(convexity)

vale = stock("VALE3.SA")

tail(vale)[1:5]
```

You can also get an investment hint for a specific stock by calling the function `hint()`.
```{r hint}
hint("VALE3.SA")
```
