---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# richer

<!-- badges: start -->
![build](https://github.com/92amartins/richer/workflows/build/badge.svg)
[![codecov](https://codecov.io/gh/92amartins/richer/branch/master/graph/badge.svg?token=0DPGPGX98O)](https://codecov.io/gh/92amartins/richer)
<!-- badges: end -->

Useful functions for stock market investments.

## Installation

You can install the development version from [GitHub](https://github.com/92amartins/richer) with:

```r
# install.packages("devtools")
devtools::install_github("92amartins/richer")
```

## Examples

Here are some use cases supported by the package.

Using the `stock()` function, you get back a `data.frame` suitable for any financial analysis.

```{r stock, message=FALSE, warning=FALSE}
library(richer)

vale = stock("VALE3.SA")

head(vale)
```

You can also get an investment hint for a specific stock by calling the function `hint()`.
```{r hint}
hint("VALE3.SA")
```


## Related Packages

`GetHFData` have long been my first choice for fetching trading data, but
the package does not work anymore as of early 2020 because of a issue with
with the B3's FTP service.

> _2020-06-30 IMPORTANT: B3 closed the public access to the ftp site and, therefore, the package is not working. As far as I know, there is no expectation of any change in that status in the near future. I'm also not aware of any other source of HF data._

So, we headed our attention to `quantmod` which fetches data from multiple sources:

> _quantmod is an R package that provides a framework for quantitative financial modeling and trading. It provides a rapid prototyping environment that makes modeling easier by removing the repetitive workflow issues surrounding data management and visualization._

## Acknowledgments
Thanks to Rodrigo Bonisem for initial discussions on this project.
