---
title: "Introduction to richer"
author: "Andrei Martins"
date: "2021-01-25"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to richer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options("getSymbols.warning4.0"=FALSE)
ggplot2::theme_set(ggplot2::theme_bw())
```

`richer` is a R package that provides useful functions for people who are willing
to invest in the stock market.

In this document we give an overview of the most important functions and common
workflows.


```{r setup, message=FALSE}
library(richer)
library(dplyr)
```

## Stock Data

`richer` provides the `stock` function which allows, fetching historical stock
prices from Yahoo Finance. You just need to inform the [stock code](https://finance.yahoo.com/quote/PETR4.SA?p=PETR4.SA).

```{r stock, warning=FALSE, message=FALSE}
petr4_prices <- stock("PETR4.SA")
print(paste(nrow(petr4_prices), "records."))
knitr::kable(head(petr4_prices))
```
From this point, you are free to carry out any sort of data analysis.

## Aggregations

The package provides a few aggregations that may come handy:
`add_monthly_variation` and `add_weekly_variation`. As their
names indicate, they provide price variation over months or
weeks respectively.

Both functions take a data.frame containing the stock prices
and a `start_date` as arguments. Then, they compute variations
from `start_date` to the current date.

Let's compute the monthly variations of `PETR4.SA` from 2020-01-01
to 2021-01-25 (the date this document was written.)

```{r agg_monthly}
petr4_prices %>%
  add_monthly_variation("2020-01-01") %>%
  knitr::kable()
```
Likewise, `add_weehly_variation` return weekly variations from the `start_date`
to the current date.

```{r agg_weekly}
petr4_prices %>%
  add_weekly_variation("2021-01-01") %>%
  knitr::kable()
```

## Graphs

Building upon the aggregation functions described above, the package
offers two functions for easy visualization: `graph` and `weekly graph`.

The former plots a graph of *monthly variations* overtime and the latter
do the same with *weekly variations*.


```{r graph, warning=FALSE, fig.width=7, fig.height=6}
graph("PETR4.SA", "2020-06-01")
```

```{r weekly_graph, warning=FALSE, fig.width=7, fig.height=6}
weekly_graph("PETR4.SA", "2021-01-01")
```

This document showcased the most important functions provided by `richer`.
For a full list of functions, install the package and type ` help(package="richer")`.


